---
title: "Coursera Regression Model Course Project"
author: "Chuk Yong"
date: "31/12/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coursera Regression Model Course Project

You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

???Is an automatic or manual transmission better for MPG???
"Quantify the MPG difference between automatic and manual transmissions"

#Start
Load dataset and understand the contents
```{r message=FALSE}
library(mtcars)
data(mtcars)
str(mtcars)
```
Transform some variables into factor form
```{r message=FALSE}
mtcars$cyl  <- factor(mtcars$cyl)
mtcars$vs   <- factor(mtcars$vs)
mtcars$am   <- factor(mtcars$am,labels=c("Auto","Man"))
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
```
## Exploratory Data Analysis
To answer the first question - ???Is an automatic or manual transmission better for MPG???, let's look at the sample and determine the averages and whether the value is signigicant. 

```{r}
mpgAuto <- subset(mtcars, mtcars$am == "Auto", select = c(mpg))
mpgMan <- subset(mtcars, mtcars$am == "Man", select = c(mpg))
t.test(mpgAuto$mpg, mpgMan$mpg)
```
We can see that:
1. Average mpg for Automatic transmission is 17.15.
2. Average mpg for Manual transmission is 24,39.
3. p-value = 0.001374

Clearly, Manual transmission has a much better mpg and the test is significant (p-value < 0.01).  


First, we explore the datasets by plotting mpg against other variables to see if there is a corelation.  Script and plots can be found in Appendix A.
From the plots, we can 

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
