---
title: "Coursera Regression Model Course Project"
author: "Chuk Yong"
date: "31/12/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coursera Regression Model Course Project

Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

“Is an automatic or manual transmission better for MPG”
"Quantify the MPG difference between automatic and manual transmissions"

Manual Transmission is better for MPG than Automatic Transmission.  The difference at first look was 7mpg or about 30% more fuel efficient in favour of Manual Transmission.  However, on further anaylsis by including other relevent factors, the difference turn out to be less.  The MPG difference between them, taking account for factors like cylinder, horse-power, displacement and weight, is around 2mpg or about 10%.    

##A study of MPG between Automatic and Manual Transmission

Load dataset and study the contents
```{r message=FALSE}
data(mtcars)
str(mtcars)
```
Transform some variables into factor form
```{r message=FALSE}
mtcars$cyl  <- factor(mtcars$cyl)
mtcars$vs   <- factor(mtcars$vs)
mtcars$am   <- factor(mtcars$am,labels=c("Auto","Man"))
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
```
## Exploratory Data Analysis

```{r}
mpgAuto <- subset(mtcars, mtcars$am == "Auto", select = c(mpg))
mpgMan <- subset(mtcars, mtcars$am == "Man", select = c(mpg))
t.test(mpgAuto$mpg, mpgMan$mpg)
```
We can see that:
1. Average mpg for Automatic transmission is 17.15.
2. Average mpg for Manual transmission is 24,39.
3. p-value = 0.001374

Clearly, Manual transmission has a much better mpg and the test is significant (p-value < 0.01).  

We can now proceed with regression modelling to see how well the is the fit.  

```{r}
fit <- lm(mpg ~ am, data = mtcars)
summary(fit)
```
As confimed by the coefficients - Manual transmission is 7.245mpg better than Autotransmission.  p-value is much less than 0.01 and so they are significant.  However, looking at R-squared and Adjusted R-squared, the value of 0.36 and 0.33 tells us that there is room for improvement.

In order to make a better decision on what other variables could possible impact mpg, we created a pair-plot, Fig 1, in Appendix A.

From the pair-plot, we can see that there are possible correlations between cyl - cylinder, disp - displacement, hp - horse power and wt - weight. 

We will fit in the variables and investigate if the introduction improves on our original fit.

#Appendix

###Pair Plot
```{r echo=FALSE}
pairs(mpg ~ ., data = mtcars, main = "Fig 1 - Pair plots of mtcars data (red:Auto, green:Manual)", pch = 21, bg = c("red","green3")[mtcars$am],oma = c(2,2,6,12))
cat("\n")
```

Figure 1 shows the pair plots between the variables in mtcars.  

##Fig2 - Plot of how R.Sqaured perform when we add in our variables
```{r echo=FALSE}
fit2 <- lm(mpg ~ am+cyl, data = mtcars)
fit3 <- lm(mpg ~ am+cyl+disp, data = mtcars)
fit4 <- lm(mpg ~ am+cyl+disp+hp, data = mtcars)
fit5 <- lm(mpg ~ am+cyl+disp+hp+wt, data = mtcars)
# Collection of r.sqared information of our fitted regression
R1 <- summary(fit)$r.squared
R2 <- summary(fit2)$r.squared
R3 <- summary(fit3)$r.squared
R4 <- summary(fit4)$r.squared
R5 <- summary(fit5)$r.squared

# Plotting r.sqaured results
rSquared <- c(R1,R2,R3,R4,R5)
Var <- c("Trans","Cyl","Disp","HP","WT")
plot(rSquared, type = "o",col = "blue", axes = FALSE, ann = FALSE)
title(main="R.Squared vs Fitted Variables", col.main="red", font.main=4)
box()
axis(1, at=1:5, lab=Var)
axis(2, las=1, at=c(0.2,0.4,0.6,0.8))
title(xlab="Variables")
title(ylab="R.Squared")
```
X-axis indicates the variables we added (cumulative) to the regression.  